### 2018-07-08 methods.tex
Update methods.tex

\begin{itemize}
        \item \gls{MSBR} design description.
	\item SERPENT2 very short overview (couple paragraphs).
	\item Full-core model description.
	\item Online reprocessing method. Advantages and disadvantages of batch-wise approach. SaltProc capabilities description.
\end{itemize}

\subsection{Saltproc}

The SaltProc tool is designed to expand SERPENT 2 depletion capabilities for modeling liquid-fueld \gls{MSR} for continuous reprocessing.
The python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
simulate continuous feeds and removals in the \gls{MSR}.

>>>>

\subsection{The SaltProc modeling and simulation code}

The SaltProc tool is designed to expand SERPENT 2 depletion capabilities for modeling liquid-fueld \gls{MSR} for continuous reprocessing.
The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
simulate continuous feeds and removals in the \gls{MSR}.
